A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-19 paper.tex
3d 2d

In this paper we consider supersymmetric Yang--Mills theories in dimensions 2 through 10. In dimensions 3 through 10 these may be obtained by dimensional reduction of the following theories: 10d $\cN=(1, 0)$ super Yang--Mills, 6d $\cN=(1, 0)$ super Yang--Mills, 4d $\cN=1$ super Yang--Mills and 3d $\cN=1$ super Yang--Mills. These theories depend on a choice of a Lie algebra $\fg$ equipped with a symmetric nondegenerate bilinear pairing. In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 these depend on a choice of an orthogonal $\fg$-representation. We do not consider superpotential and mass terms in this paper. Moreover, as we are working perturbatively, we ignore all topological terms ($\theta$-terms).

@@

Given a classical BRST theory $\cM$, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_g$.
\brian{
Why $S_g$? I suggest $S_0$, or $S_\cM$, or $S_{\rm cot}$. Also it's not clear from this sentence how $S_g$ depends on the data of the BRST theory. It doesn't use $S_{BRST}$, for instance.
} 
Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter. Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_g, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.

\begin{definition}
Let $(\cM, S_{\mr{BRST}})$ be a classical BRST theory. The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_g$.
\end{definition}

@@

\begin{lemma} \label{lem:YM1}
One has $\{S_{\rm SYM}, I^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
\end{lemma}
\begin{proof}
Let us decompose $S_{\matter}=\sum_{i=1}^5 S_{\matter, i}$ into the individual summands in Equation \eqref{matteraction}.

@@

\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
We will now consider 3d $\mc N=4$ theories, which arise by dimensional reduction from 4d $\mc N=2$ super Yang-Mills with gauge group $G$, coupled to a hypermultiplet valued in a symplectic representation $U$, or equivalently by dimensional reduction from 6d $\mc N=(1,0)$ super Yang-Mills coupled to a hypermultiplet.  The $R$-symmetry group is $G_R = \Spin(4;\CC)$, and $W$ is its defining representation.

@@

\subsubsection{Minimal Twist}
\label{sect:3d_4_minimal_twist}
The 3d $\cN=4$ super Yang--Mills viewed as a $\cN=2$ supersymmetric theory coincides with the 3d $\cN=2$ super Yang--Mills with matter valued in the representation $R = U \oplus \gg$.

@@

\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d8section}
Finally, let's consider maximal super Yang-Mills theory with gauge group $G$ in dimension 3, with $\mc N=8$ supersymmetry.  This is the theory obtained by compactifying $\mc N=(1,0)$ super Yang-Mills on $\RR^{10}$ down to $\RR^3$.  
The $R$-symmetry group is $G_R = \Spin(7;\CC)$, and $W$ is its $8$-dimensional (Dirac) spin representation.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.  The fields we obtain are
\begin{itemize}
 \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and seven scalar fields $\phi_i \in \Omega^0(\RR^3; \gg)$.
 \item Fermions: eight spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$.
 \item Ghost Field: $c \in \Omega^0(\RR^3;\gg)[1]$.
\end{itemize}

In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in $\mc N=4$.  That is, there are three orbits: one consisting of rank 1 supercharges, and two orbits of rank 2 supercharges.  We can see this in the following way.
\begin{lemma}
There are two distinct $\spin(3;\CC) \times G_R$-orbits of square-zero supercharges of rank $2$ in the 3d $\mc N=8$ supersymmetry algebra.
\end{lemma}

@@

\subsubsection{Minimal Twist}
\label{sect:3d8minimal_twist}
The 3d $\cN=8$ super Yang--Mills viewed as an $\cN=4$ supersymmetric theory coincides with the 3d $\cN=4$ super Yang--Mills with matter valued in the representation $U = T^*\gg$.  
Alternatively, it is obtained by dimensional reduction from the holomorphic twist of 4d $\mc N=4$ super Yang-Mills.

@@

\begin{theorem} \label{3d_8_A_twist_thm}
The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$. Moreover, this equivalence is $\U(1)$-equivariant.
\end{theorem}

@@

\begin{theorem} \label{3d_8_B_twist_thm}
The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. %Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
\end{theorem}

@@

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with Matter} \label{sect:2d(2,2)}
First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.  
This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  
The R-symmetry group is $G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$, with the factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$. \brian{Not sure what $(a^{-1},b^{-1})$ means? Do you mean $(-a,-b)$?}

@@

In the $\mc N=(2,2)$ supersymmetry algebra there is are three classes of non-trivial orbits of square-zero supercharges.  
\begin{itemize}
 \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic.  
There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$ acting with weight $1$ on $S_+$ and weight $-1$ acting on $S_-$.  
 \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times (\CC^\times \times \CC^\times)$.  Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors~

@@

To deform the holomorphic twist to the topological A-twist, obtaining a Hodge deformation, we use similar techniques to those of Section \ref{sect:4d2Donaldson}.  We first analyze how the supersymmetry action decomposes.  Consider the 1-parameter family of supercharges
\begin{equation} \label{eq:2dHodgefamily}
Q_t = Q_0 + tQ',
\end{equation}
where $Q_0 = (1,i) \in S_+$ is a holomorphic supercharge, and $Q' = (1,i) \in S_-$.  This family of supercharges are all compatible with the twisting homomorphism $\phi_A$ -- the map $\U(1) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$.  They are promoted to twisting data using the homomorphism $\phi_B$ with weights $(1,-1)$.  Let us first decompose our fields according to the twisting homomorphism $\phi_A$.  The fields we obtain are given as follows, where the subscripts denote the $\mr U(1)$-weight.
%\begin{itemize}
% \item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $\chi_1 \in \Omega^0(\CC ; \fg[2])$, $\chi_{-1} \in \Omega^0(\CC ; \fg[2])$. 
% %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
% \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
% %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
% \item $\gg$-valued fermions: $(\lambda_2, \lambda_0, \lambda'_{0}, \lambda_{-2}) \in \Omega^0(\RR^2 ; \gg[-1] \oplus \gg[-1] \oplus \gg[1] \oplus \gg[1])$.
% \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
% \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
%\end{itemize}

\begin{itemize}
\item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Tilde{a} \in \Omega^0(\CC ; \fg)[2]$. 
\item $\gg$-valued fermions: $\lambda_0 \in \Omega^{0}(\CC ; \fg)[-1]$, $\chi_{0,1} \in \Omega^{0,1}(\CC ; \fg) [1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg)[1]$, $\Tilde{\lambda}_0 \in \Omega^0(\CC ; \fg) [3]$.
 %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
 \item  $R$-valued bosons: $\gamma_0 \in \Omega^0(\CC ; R)$, $\phi \in \Omega^0(\CC ; R^*)$;
 %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item $R$-valued fermions: $\gamma_{0,1} \in \Omega^{0,1}(\CC ; R)[-1]$, $\Tilde{\psi}_0 \in \Omega^0(\CC ; R)[1]$, $\beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)[-1]$, $\psi \in \Omega^0(\CC ; R^*)[1]$; 
 \item Ghost field: $c \in \Omega^0(\RR^2; \fg)[1]$.
\end{itemize}
We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.

@@

\begin{theorem} \label{2d_2_A_twist_thm}
The topological A-twist of 2d $\mc N=(2,2)$ super Yang-Mills theory with gauge group $G$ coupled to the $\mc N=(2,2)$ chiral multiplet valued in a representation $R$ is perturbatively equivalent, as a one-parameter deformation of the holomorphic twist, to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.  This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\subsubsection{Topological B Twist} \label{sect:2d22Btwist}

@@

\begin{proof}
We again dimensionally reduce the holomorphic twist of 3d $\mc N=2$ super Yang-Mills, but this time in one of the non-invariant directions.  That is, we start with the result from Theorem \ref{3d_minimal_twist_thm}, then apply Proposition \ref{CS_diml_red_prop} to turn the complex direction into a second real de Rham direction.
\end{proof}

\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with Matter} \label{sect:2d(4,4)}
We can likewise consider $\mc N=(4,4)$ super Yang-Mills theory with gauge group $G$, with a hypermultiplet valued in a symplectic representation $U$, by dimensionally reducing 3d $\mc N=4$ super Yang-Mills.  No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.

The R-symmetry group in the $\mc N=(4,4)$ case is $G_R = \SU(2) \times \spin(4;\CC)$, where $\spin(4;\CC)$ acts on $S_+ \otimes W_+ \oplus S_- \otimes W_- \iso S_+^6 \otimes W_+^6$ -- where $W_+^6$ is the 6d $\mc N=(1,0)$ auxiliary space -- by its fundamental representation on both $W_+$ and $W_-$, and where $\SU(2)$ acts by permuting the two factors, i.e. by its fundamental representation on $W^6$.

@@

\begin{prop}
There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(4,4)$ supersymmetry algebra, which we will refer to as the A- and B-supercharges.  The B-supercharge occurs as a degeneration of A-type supercharges.
\end{prop}

\begin{proof}
First, let us decompose the 6d semispinor representation $S_+^6$ into $S_+^4 \oplus S_-^4$ as a representation of $\spin(4;\CC)$. A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$ and a pair of null vectors in $W_+^6$, all non-zero.  There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are colinear, or they are distinct.  We will refer to these as the B- and A-supercharges respectively.
\end{proof}

Upon dimensional reduction from 3d $\mc N=4$, the B-supercharge reduced to the 2d $\mc N=(4,4)$ B-supercharge.  Indeed, the 3d B-supercharge squares to zero as an element of the 6d $\mc N=(1,0)$ supersymmetry algebra, which means that in this 6d algebra it has rank 1.  Therefore the two vectors in $W_+^6$ discussed above must be colinear.

\subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
We obtain the following from the 3d $\mc N=4$ minimal twist of Theorem \ref{3d_4_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

@@

\subsubsection{Topological A Twist} \label{sect:2d44Atwist}
We likewise obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

@@

\subsubsection{Topological B Twist} \label{sect:2d44Btwist}
Finally, we obtain the following from the 3d $\mc N=4$ A-twist of Theorem \ref{3d_4_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

@@

\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with Matter} \label{sect:2d(8,8)}
Now, let us consider $\mc N=(8,8)$ super Yang-Mills theory by dimensionally reducing 3d $\mc N=8$ super Yang-Mills, or we can consider $\mc N=(8,8)$ super Yang-Mills.  No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.

@@

\subsubsection{Minimal Twist} \label{sect:2d88minimaltwist}
We obtain the following from the 3d $\mc N=8$ minimal twist of Theorem \ref{3d_8_minimal_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

@@

\subsubsection{Topological A Twist} \label{sect:2d88Atwist}
We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_A_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

@@

\subsubsection{Topological B Twist} \label{sect:2d88Btwist}
We obtain the following from the 3d $\mc N=8$ A-twist of Theorem \ref{3d_8_B_twist_thm} by dimensional reduction, i.e. by applying Proposition \ref{CS_to_BF_diml_red_prop}.

>>>>

In this paper we consider supersymmetric Yang--Mills theories in dimensions 2 through 10. In dimensions 3 through 10 these may be obtained by dimensional reduction of the following theories: 10d $\cN=(1, 0)$ super Yang--Mills, 6d $\cN=(1, 0)$ super Yang--Mills, 4d $\cN=1$ super Yang--Mills and 3d $\cN=1$ super Yang--Mills. These theories depend on a choice of a Lie algebra $\fg$ equipped with a symmetric nondegenerate bilinear pairing. In addition, in dimensions 6, 4 and 3 we may add matter multiplets: in dimension 6 these depend on a choice of a symplectic $\fg$-representation (a hypermultiplet), in dimension 4 these depend on a choice of a $\fg$-representation (a chiral multiplet) and in dimension 3 these depend on a choice of an orthogonal $\fg$-representation. We do not consider superpotential, mass, or Fayet--Iliopoulos terms in this paper. Moreover, as we are working perturbatively, we ignore all topological terms ($\theta$-terms).

@@

Given a classical BRST theory $\cM$, we may consider the cotangent theory $T^*[-1]\cM$ whose action functional we denote by $S_{\rm anti}$.
Let us denote the pullback of $S_{\mathrm{BRST}}$ along the obvious projection $T^*[-1]\cM\rightarrow \cM$ by the same letter. Then the equation $Q_{\mathrm{BRST}} S_{\mathrm{BRST}} = 0$ in $\oloc(\cM)$ implies that $\{S_{\rm anti}, S_{\mathrm{BRST}}\} = 0$ in $\oloc(T^*[-1]\cM)$.

\begin{definition}
Let $(\cM, S_{\mr{BRST}})$ be a classical BRST theory. The \defterm{associated classical BV theory} is the $(-1)$-shifted cotangent bundle $T^*[-1]\cM$ equipped with its natural $(-1)$-shifted symplectic structure and the action functional $S_{\mathrm{BRST}} + S_{\rm anti}$.
\end{definition}

@@

\begin{lemma} \label{lem:YM1}
One has $\{S_{\rm SYM}, S^{(1)}\} (Q) = 0$ for all $Q \in \Sigma$. 
\end{lemma}
\begin{proof}
Let us decompose $S_{\matter}=\sum_{i=1}^5 S_{\matter, i}$ into the individual summands in Equation \eqref{matteraction}.

@@

\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang-Mills with Hypermultiplet Matter} \label{3d_4_section}
Next, consider 3d $\mc N=4$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 4d $\mc N=2$ supersymmetric Yang--Mills theory; or equivalently by dimensional reduction of 6d $\mc N=(1,0)$ supersymmetric Yang--Mills theory. 
The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the defining representation.

@@

\subsubsection{Minimal Twist}
\label{sect:3d_4_minimal_twist}
Note that 3d $\cN=4$ supersymmetric Yang--Mills theory, viewed as a $\cN=2$ supersymmetric theory, coincides with 3d $\cN=2$ supersymmetric Yang--Mills theory with matter valued in the representation $R = U \oplus \gg$.

@@

\subsection{\texorpdfstring{$\cN = 8$}{N=8} Super Yang-Mills Theory} \label{3d8section}
Finally, consider maximally supersymmetric Yang--Mills theory in dimension 3.
This theory is the dimensional reduction of 10d $\cN = (1,0)$ supersymmetric Yang--Mills theory.  
The $R$-symmetry group is $G_R = \Spin(7;\CC)$, where $W$ is the $8$-dimensional (Dirac) spin representation.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST fields of $\mc N=8$ supersymmetric Yang--Mills theory by restricting the 4d fields from Section \ref{4d_4_section} to representations of the group $\spin(3;\CC)$.  
The fields are:
\begin{itemize}
 \item Bosons: $A \in \Omega^1(\RR^3; \gg)$, and scalar fields $\phi_j \in \Omega^0(\RR^3; \gg)$, $j=1,\ldots, 7$.
 \item Fermions: spinor fields $\lambda_i \in \Omega^0(\RR^3; S \otimes \gg)$, $i=1,\ldots, 8$.
 \item Ghost Field: $c \in \Omega^0(\RR^3;\gg)[1]$.
\end{itemize}

In the $\mc N=8$ supersymmetry algebra the classification of twists is the same as we saw in 3d $\mc N=4$.  
There are three orbits: one consisting of rank 1 supercharges, and two orbits of rank 2 supercharges.  We can see this in the following way.
\begin{lemma}
There are two distinct $\spin(3;\CC) \times G_R$-orbits of square-zero supercharges of rank $2$ in the 3d $\mc N=8$ supersymmetry algebra.
\end{lemma}

@@

\subsubsection{Minimal Twist}
\label{sect:3d8minimal_twist}
The 3d $\cN=8$ supersymmetric Yang--Mills theory, viewed as an $\cN=4$ supersymmetric theory, coincides with the 3d $\cN=4$ supersymmetric Yang--Mills theory with matter valued in the symplectic representation $U = T^*\gg$.  
Alternatively, it is obtained by dimensional reduction of 4d $\mc N=4$ supersymmetric Yang--Mills theory.

@@

\begin{theorem} \label{3d_8_A_twist_thm}
The twist of 3d $\cN=8$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges is perturbatively equivalent to the generalized Hodge theory $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, (\gg/\gg)_{\mr{Hod}})$. Moreover, this equivalence is $\U(1)$-equivariant.
\end{theorem}
\brian{Need to explain what happened to $\Sect$}

@@

\begin{theorem} \label{3d_8_B_twist_thm}
The rank $2$ B-twist of 3d $\mc N=8$ super Yang-Mills theory with gauge group $G$ is perturbatively equivalent to the BF theory with space of fields $T^*[-1]\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)$. %Moreover, this equivalence is $\spin(3;\RR)$-equivariant.
\end{theorem}
\brian{Need to explain what happened to $\Sect$}

@@

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with Matter} \label{sect:2d(2,2)}
First, consider 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 3d $\mc N=2$ supersymmetric Yang--Mills theory.  
%This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  
The R-symmetry group is $$G_R = \ZZ/2\ZZ \ltimes (\spin(2;\CC) \times \spin(2;\CC)) \iso \ZZ/2 \ltimes ( \CC^\times \times \CC^\times)$$ with the $\CC^\times$-factors acting by their vector representation on $W_+ \cong \CC^2$ and $W_- \cong \CC^2$ respectively, and with $\ZZ/2\ZZ$ acting on both $W_+$ and $W_-$ by $(a,b) \mapsto (a^{-1}, b^{-1})$. \brian{Not sure what $(a^{-1},b^{-1})$ means? Do you mean $(-a,-b)$?}

@@

In the $\mc N=(2,2)$ supersymmetry algebra there are three classes of non-trivial orbits of square-zero supercharges.  
\begin{itemize}
 \item Square-zero supercharges of rank $(1,0)$ or $(0,1)$, which are holomorphic.  
There is a compatible twisting homomorphism from $\mr U(1)$, and a compatible twisting datum $\alpha \colon \mr U(1) \to \spin(2;\RR)$ acting with weight $1$ on $S_+$ and weight $-1$ acting on $S_-$.  
 \item Square-zero supercharges of rank $(1,1)$ are topological, and split into four orbits under the action of $\spin(2;\CC) \times (\CC^\times \times \CC^\times)$.  Indeed, we can identify a square-zero supercharge of rank $(1,1)$ as a pair of vectors~

@@

To deform the holomorphic twist to the topological A-twist, obtaining a Hodge deformation, we use similar techniques to those of Section \ref{sect:4d2Donaldson}.  We first analyze how the supersymmetry action decomposes.  Consider the 1-parameter family of supercharges
\begin{equation} \label{eq:2dHodgefamily}
Q_t = Q_0 + tQ',
\end{equation}
where $Q_0 = (1,i) \in S_+$ is a holomorphic supercharge, and $Q' = (1,i) \in S_-$.  This family of supercharges are all compatible with the twisting homomorphism $\phi_A$ -- the map $\U(1) \to \spin(2;\CC) \times \spin(2;\CC)$ with weights $(1,1)$.  They are promoted to twisting data using the homomorphism $\phi_B$ with weights $(1,-1)$.  Let us first decompose our fields according to the twisting homomorphism $\phi_A$:
%The fields we obtain are given as follows, where the subscripts denote the $\mr U(1)$-weight.
%\begin{itemize}
% \item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $\chi_1 \in \Omega^0(\CC ; \fg[2])$, $\chi_{-1} \in \Omega^0(\CC ; \fg[2])$. 
% %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
% \item  $R$-valued bosons: $\phi_0 \in \Omega^0(\CC ; R)$,  $\ol \phi_0 \in \Omega^0(\CC ; R^*)$.
% %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
% \item $\gg$-valued fermions: $(\lambda_2, \lambda_0, \lambda'_{0}, \lambda_{-2}) \in \Omega^0(\RR^2 ; \gg[-1] \oplus \gg[-1] \oplus \gg[1] \oplus \gg[1])$.
% \item $R$-valued fermions: $(\psi_1, \psi_{-1}, \ol \psi_1, \ol \psi_{-1}) \in \Omega^0(\RR^2 ; R[-1] \oplus R[-1] \oplus R^*[1] \oplus R^*[1])$.
% \item Ghost field: $c_0 \in \Omega^0(\RR^2; \gg[1])$.
%\end{itemize}

\begin{itemize}
\item $\gg$-valued bosons: $A_{1,0} \in \Omega^{1,0}(\CC; \fg)$, $A_{0,1} \in \Omega^{0,1} (\CC ; \fg)$, $a \in \Omega^0(\CC ; \fg)[2]$, $\Tilde{a} \in \Omega^0(\CC ; \fg)[2]$. 
\item $\gg$-valued fermions: $\lambda_0 \in \Omega^{0}(\CC ; \fg)[-1]$, $\chi_{0,1} \in \Omega^{0,1}(\CC ; \fg) [1]$, $\lambda_{1,0} \in \Omega^{1,0}(\CC ; \fg)[1]$, $\Tilde{\lambda}_0 \in \Omega^0(\CC ; \fg) [3]$.
 %$\chi_1 \in \Omega$(A_1, A_{-1}, \chi_1, \chi_{-1}) \in \Omega^0(\RR^2; \gg^2 \oplus \gg[-2] \oplus \gg[-2])$.
 \item  $R$-valued bosons: $\gamma_0 \in \Omega^0(\CC ; R)$, $\phi \in \Omega^0(\CC ; R^*)$;
 %$R$-valued bosons: $(\phi_0, \ol \phi_0) \in \Omega^0(\RR^2 ; R \oplus R^*)$.
 \item $R$-valued fermions: $\gamma_{0,1} \in \Omega^{0,1}(\CC ; R)[-1]$, $\Tilde{\psi}_0 \in \Omega^0(\CC ; R)[1]$, $\beta_{1,0} \in \Omega^{1,0}(\CC ; R^*)[-1]$, $\psi \in \Omega^0(\CC ; R^*)[1]$; 
 \item Ghost field: $c \in \Omega^0(\RR^2; \fg)[1]$.
\end{itemize}
%We write the antifields similarly: the antifield of a field $x_n$ is written $x^*_{-n}$, with opposite $\mr U(1)$-weight.

@@

\begin{theorem} \label{2d_2_A_twist_thm}
The topological 2d $\mc N=(2,2)$ supersymmetric Yang--Mills theory with respect to the family of square-zero supercharges $Q_t$ is perturbatively equivalent to the Hodge family with moduli space $T^*[-1]\mr{Map}(\CC, (R/\gg)_{\mr{Hod}})$.  
This equivalence is $\mr U(1)$-invariant.
\end{theorem}

@@

\begin{corollary}
The topological $A$-twist of 2d $\cN=(2,2)$-supersymmetric Yang--Mills theory is perturbatively trivial.
\end{corollary}

\subsubsection{Topological $B$-Twist} \label{sect:2d22Btwist}

@@

\begin{proof}
We dimensionally reduce the holomorphic twist of 3d $\mc N=2$ super Yang-Mills in a non-invariant direction.  
Combining Theorem \ref{3d_minimal_twist_thm} and Proposition \ref{CS_diml_red_prop} to turn the we obtain the desired result.
\end{proof}

\subsection{\texorpdfstring{$\cN=(4,4)$}{N=(4,4)} Super Yang-Mills with Matter} \label{sect:2d(4,4)}
Next, we consider $\mc N=(4,4)$ supersymmetric Yang--Mills theory.
This theory is obtained as the dimension reduction of 3d $\mc N=4$ supersymmetric Yang--Mills theory.  
No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.

The R-symmetry group is $G_R = \SU(2) \times \spin(4;\CC)$ whose action on $\Sigma = S_+ \otimes W_+ \oplus S_- \otimes W_-$ can be described as follows.
First, $\spin(4;\CC)$ acts on $W_+$ and $W_-$ by the fundamental and anti-fundamental representations, respectively.
The group $\SU(2)$ acts by permuting the two factors.

@@

\begin{prop}
There are two $G_R$-orbits in the space of rank $(1,1)$ square-zero supercharges in the $\mc N=(4,4)$ supersymmetry algebra, which we will refer to as the $A$- and $B$-supercharges.  The $B$-supercharge occurs as a degeneration of $A$-type supercharges.
\end{prop}

\begin{proof}
Decompose the 6d semispinor representation $S_+^6$ into $S_+^4 \oplus S_-^4$ as a representation of $\spin(4;\CC)$. 
A rank $(1,1)$ square-zero supercharge can be identified with the data of a null vector in $S_+^4$, a null vector in $S_-^4$, and a pair of null vectors in $W_+^6$, all non-zero.  
There are only two $G_R$-orbits in this space of quadruples of null vectors: either the two null vectors in $W_+^6$ are colinear, or they are distinct.  
These are the $B$- and $A$-supercharges respectively.
\end{proof}

Upon dimensional reduction from 3d $\mc N=4$, the $B$-supercharge reduces to the 2d $\mc N=(4,4)$ $B$-supercharge.  
Indeed, the 3d $B$-supercharge squares to zero as an element of the 6d $\mc N=(1,0)$ supersymmetry algebra, which means that in this 6d algebra it has rank 1.  
Therefore the two vectors in $W_+^6$ discussed above must be colinear.

\subsubsection{Minimal Twist} \label{sect:2d44minimaltwist}
The minimal twist is obtained as the dimensional reduction of the minimal twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
By Theorem \ref{3d_4_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.

@@

\subsubsection{Topological A Twist} \label{sect:2d44Atwist}
The topological $A$-twist is obtained as the dimensional reduction of the $A$-twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
By Theorem \ref{3d_4_A_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.

@@

\subsubsection{Topological B Twist} \label{sect:2d44Btwist}

The topological $B$-twist is obtained as the dimensional reduction of the $B$-twist of 3d $\mc N=4$ supersymmetric Yang--Mills theory.
By Theorem \ref{3d_4_B_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.

@@

\subsection{\texorpdfstring{$\cN=(8,8)$}{N=(8,8)} Super Yang-Mills with Matter} \label{sect:2d(8,8)}
Next we consider $\mc N=(8,8)$ supersymmetric Yang--Mills theory.
This theory is the dimensional reduction of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
No new twists arise, i.e. every square-zero supercharge sits inside an $\mc N=(2,2)$ subalgebra.

@@

\subsubsection{Minimal Twist} \label{sect:2d88minimaltwist}
The minimal twist is obtained by the dimensional reduction of the minimal twist of 3d $\mc N=8$ supersymmetric Yang--Mills theory.
Combining Theorem \ref{3d_8_minimal_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we have the following.

@@

\subsubsection{Topological A Twist} \label{sect:2d88Atwist}
The topological $A$-twist is obtained as the dimensional reduction of the $A$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
Combining Theorem \ref{3d_8_A_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.

@@

\subsubsection{Topological B Twist} \label{sect:2d88Btwist}
The topological $B$-twist is obtained as the dimensional reduction of the $B$-twist of 3d $\cN = 8$ supersymmetric Yang--Mills theory.
Combining Theorem \ref{3d_8_B_twist_thm} and Proposition \ref{CS_to_BF_diml_red_prop} we obtain the following.
